A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-10-29 paper/main.tex
Reword conclusions

\section*{Conclusions}
% what the paper is about
As an extension of the studyforrest dataset, we present an annotation of spoken
language in the two hours lasting ``research cut'' of the audio-visual movie
``Forrest Gump'' and its temporally aligned audio-description.
% what we did
We annotated the onset and offset of sentences, words and phonemes, and the
corresponding speaker's identity.
% what for
An additional tagging of each word's linguistic features enables independent
working groups to create models of hemodynamic activity
correlating with linguistics aspects like phonetics, grammar, syntax, and
semantics occurring in two naturalistic stimuli.
% results
Results of our analysis that we ran to assess the dataset's quality shows that
the annotation's content can indeed be used to isolate speech-related networks
in the human brain under life-like conditions.

>>>>

\section*{Conclusions}
% what the paper is about
As an extension of the studyforrest dataset, we present an annotation of spoken
language in the two-hours audio-visual movie
``Forrest Gump'' and its temporally aligned audio-description.
% what we did
We annotated the onset and offset of sentences, words and phonemes, and the
corresponding speaker's identity.
% what for
An additional tagging of each word's linguistic features enables creating models
of hemodynamic activity
correlating with linguistics aspects like phonetics, grammar, syntax, and
semantics occurring in two naturalistic stimuli.
% results
Results of our analysis indicate that
the annotation's content can be used to locate speech-related networks
in the human brain under life-like conditions.
